Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-28 Manuscript_draft.Rmd
Update Q2.1 plot and removed Q2.1 table for now

png(file = 'forest_meta_Q2_1_precision.png', width = 600, height = 480)

forest(q2_1_asymp_precision, sortvar = -seTE, overall = FALSE)

@@

#get data
Q2_1_table <- httr::content(response2_1)

#clean countries
Q2_1_table <- Q2_1_table %>%
  mutate(country = ifelse(country == 10, "Australia", country),
         country = ifelse(country == 11, "Austria", country),
         country = ifelse(country == 15, "Bahrain", country),
         country = ifelse(country == 19, "Belgium", country),
         country = ifelse(country == 28, "Brunei", country),
         country = ifelse(country == 34, "Canada", country),
         country = ifelse(country == 40, "China", country),
         country = ifelse(country == 41, "Colombia", country),
         country = ifelse(country == 51, "Denmark", country),
         country = ifelse(country == 62, "France", country),
         country = ifelse(country == 63, "French Guyana", country),
         country = ifelse(country == 67, "Germany", country),
         country = ifelse(country == 69, "Greece", country),
         country = ifelse(country == 78, "Iceland", country),
         country = ifelse(country == 79, "India", country),
         country = ifelse(country == 83, "Ireland", country),
         country = ifelse(country == 85, "Italy", country),
         country = ifelse(country == 87, "Japan", country),
         country = ifelse(country == 92, "Kuwait", country),
         country = ifelse(country == 105, "Malaysia", country),
         country = ifelse(country == 121, "Netherlands", country),
         country = ifelse(country == 128, "Norway", country),
         country = ifelse(country == 888, "Other", country),
         country = ifelse(country == 138, "Portugal", country),
         country = ifelse(country == 146, "Saudi Arabia", country),
         country = ifelse(country == 157, "South Korea", country),
         country = ifelse(country == 160, "Spain", country),
         country = ifelse(country == 174, "Turkey", country),
         country = ifelse(country == 176, "Uganda", country),
         country = ifelse(country == 180, "United Kingdom", country),
         country = ifelse(country == 181, "United States of America", country),
         country = ifelse(country == 185, "Vietnam", country))
#clean regions

Q2_1_table$region[Q2_1_table$region == "none" | Q2_1_table$region == "None."] <- NA
#create location variable
Q2_1_table$location <- Q2_1_table$country
Q2_1_table <- Q2_1_table %>%
  mutate(location = ifelse(!is.na(region), paste0(country, ", ", region), country))
#drop country and region variables
Q2_1_table$country <- NULL
Q2_1_table$region <- NULL

#author column
Q2_1_table$study <- paste0(Q2_1_table$author_1, " (", Q2_1_table$year, ")")
Q2_1_table$author_1 <- NULL
Q2_1_table$record_id <- NULL
Q2_1_table$year <- NULL

#clean settings
Q2_1_table$setting <- "Not available"
Q2_1_table <- Q2_1_table %>%
  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
         setting = ifelse(setting2 == 4, "Statistical model", setting),
         setting = ifelse(setting2 == 5, "Screening", setting),
         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
         setting = ifelse(setting2 == 10, "Screening: general population", setting),
         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
Q2_1_table$setting2 <- NULL

#reorder columns
Q2_1_table <- data.frame(Q2_1_table$study,
                         Q2_1_table$setting,
                         Q2_1_table$location)

names(Q2_1_table) <- c("study", "setting", "location")

>>>>

png(file = 'forest_meta_Q2_1.png', width = 600, height = 300)

@@

#table not necessary - all studies in q2.1 described in full table on q1, and numbers are in forest plot

#get data
#Q2_1_table <- httr::content(response2_1)

#clean countries
#Q2_1_table <- Q2_1_table %>%
 # mutate(country = ifelse(country == 10, "Australia", country),
  #       country = ifelse(country == 11, "Austria", country),
  #       country = ifelse(country == 15, "Bahrain", country),
  #       country = ifelse(country == 19, "Belgium", country),
  #       country = ifelse(country == 28, "Brunei", country),
  #       country = ifelse(country == 34, "Canada", country),
  #       country = ifelse(country == 40, "China", country),
  #       country = ifelse(country == 41, "Colombia", country),
  #       country = ifelse(country == 51, "Denmark", country),
  #       country = ifelse(country == 62, "France", country),
  #       country = ifelse(country == 63, "French Guyana", country),
  #       country = ifelse(country == 67, "Germany", country),
  #       country = ifelse(country == 69, "Greece", country),
  #       country = ifelse(country == 78, "Iceland", country),
  #       country = ifelse(country == 79, "India", country),
  #       country = ifelse(country == 83, "Ireland", country),
  #       country = ifelse(country == 85, "Italy", country),
  #       country = ifelse(country == 87, "Japan", country),
  #       country = ifelse(country == 92, "Kuwait", country),
  #       country = ifelse(country == 105, "Malaysia", country),
  #       country = ifelse(country == 121, "Netherlands", country),
  #       country = ifelse(country == 128, "Norway", country),
  #       country = ifelse(country == 888, "Other", country),
  #       country = ifelse(country == 138, "Portugal", country),
  #       country = ifelse(country == 146, "Saudi Arabia", country),
  #       country = ifelse(country == 157, "South Korea", country),
  #       country = ifelse(country == 160, "Spain", country),
  #       country = ifelse(country == 174, "Turkey", country),
  #       country = ifelse(country == 176, "Uganda", country),
  #       country = ifelse(country == 180, "United Kingdom", country),
  #       country = ifelse(country == 181, "United States of America", country),
  #       country = ifelse(country == 185, "Vietnam", country))
#clean regions

#Q2_1_table$region[Q2_1_table$region == "none" | Q2_1_table$region == "None."] <- NA
#create location variable
#Q2_1_table$location <- Q2_1_table$country
#Q2_1_table <- Q2_1_table %>%
#  mutate(location = ifelse(!is.na(region), paste0(country, ", ", region), country))
#drop country and region variables
#Q2_1_table$country <- NULL
#Q2_1_table$region <- NULL

#author column
#Q2_1_table$study <- paste0(Q2_1_table$author_1, " (", Q2_1_table$year, ")")
#Q2_1_table$author_1 <- NULL
#Q2_1_table$record_id <- NULL
#Q2_1_table$year <- NULL

#clean settings
#Q2_1_table$setting <- "Not available"
#Q2_1_table <- Q2_1_table %>%
 # mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
#         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
#         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
#         setting = ifelse(setting2 == 4, "Statistical model", setting),
#         setting = ifelse(setting2 == 5, "Screening", setting),
#         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
#         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
#         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
#         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
#         setting = ifelse(setting2 == 10, "Screening: general population", setting),
#         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
#Q2_1_table$setting2 <- NULL

#reorder columns
#Q2_1_table <- data.frame(Q2_1_table$study,
 #                        Q2_1_table$setting,
#                         Q2_1_table$location)

#names(Q2_1_table) <- c("study", "setting", "location")
